BIP Architectures and Open pNets

### 2019-01-29 2018-Arch-pNets/arch-pNets.tex
encore un pb de synchro ?

%% CTL
\newcommand{\AG}[1][\ ]{\ensuremath{\mathtt{AG}#1}}
\newcommand{\AF}[1][\ ]{\ensuremath{\mathtt{AF}#1}}
\newcommand{\EF}[1][\ ]{\ensuremath{\mathtt{EF}#1}}
\newcommand{\AW}[3][\ ]{\ensuremath{\mathtt{A}\left[#2\ \mathtt{W}\ #3\right]#1}}
\newcommand{\EU}[3][\ ]{\ensuremath{\mathtt{E}\left[#2\ \mathtt{U}\ #3\right]#1}}

@@

\addSB{Although we define properties as state predicates, any
  appropriate logic can be used to specify them.  For instance, the
  property \emph{``There is always a possibility to reset the system
    or resume operation after a single failure'' (\ie without
    additional failures occuring in the meantime)} enforced by the
  Failure Monitor architecture can be specified using CTL as $\AG
  \bigl(\PortFail \rightarrow \EU[]{\lnot \PortFail}{(\PortResume \lor
    \PortReset)}\bigr)$.  Additional properties are provided in
  \app{properties}.}

@@

@@

The architecture in \fig{schema:ArchFailure:BIP} enforces the
following safety properties:
\begin{enumerate}
\item There is always a possibility to reset the system or resume
  operation after a single failure (\ie without additional failures
  occuring in the meantime):
  \begin{equation}
    \label{eq:prop:reset:can}
    \AG \bigl(\PortFail \rightarrow \EU[]{\lnot \PortFail}{(\PortResume \lor \PortReset)}\bigr).
  \end{equation}

>>>>

%% CTL
\newcommand{\AG}[1][\ ]{\ensuremath{\mathtt{AG}#1}}
\newcommand{\AF}[1][\ ]{\ensuremath{\mathtt{AF}#1}}
\newcommand{\EF}[1][\ ]{\ensuremath{\mathtt{EF}#1}}
\newcommand{\AW}[3][\ ]{\ensuremath{\mathtt{A}\left[#2\ \mathtt{W}\ #3\right]#1}}

@@

\addSB{Although we define properties as state predicates, any
  appropriate logic can be used to specify them.  For instance, the
  property \emph{``There is always a possibility to reset the system
    after a failure''} enforced by the Failure Monitor architecture
  can be specified using CTL as $\AG (\PortFail \rightarrow \EF
  \PortReset)$.  Additional properties are provided in \app{properties}.}

@@

\begin{indent}
  description courte et intuitive avec reference au papier d'Avocs
\end{indent}

@@

The architecture in \fig{schema:ArchFailure:BIP} enforces the
following safety properties:
\begin{enumerate}
\item There is always a possibility to reset the system after a
  failure:
  \begin{equation}
    \label{eq:prop:reset:can}
    \AG (\PortFail \rightarrow \EF \PortReset).
  \end{equation}
